\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
beginning abstract
abstract

\begin{abstract} ...
\end{abstract}

>>>>

\begin{abstract}
Software Defined Networking (SDN) is a new paradigm that gives programmers 
centralized visibility and control over the network. However, due to performance 
demands, writing correct and efficient programs is challenging. Programmers must 
reason about how to correctly forward packets in the network, how to maintain
global network state, which packets to observe at the centralized controller, 
and how to minimize latency by pushing as much decision logic
as possible onto the high-performance switch elements.

We introduce a high-level SDN library that can be embedded into existing languages.
Our library exposes an API that allows programmers to directly express behavioral intent, 
while leaving the performance details to the library's optimization algorithms.
Our library supports basic tests on packet fields as well as a simple mutable table
data structure for storing global network information (e.g., firewall ACL, MAC learning table).
Finally, to ensure adequate performance, 
we statically analyze the programmer's policy by pushing symbolic packets through the policy 
and observing the resulting packet forwarding decision.

\end{abstract}
